The SMT Competition 2015--2018

### 2019-03-22 2018/report/SMT-COMP.tex
Add scripts for application track bar plots.

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics in the
  Main track.}
  \label{fig:progress}
\end{figure}

>>>>

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Main_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics in the
  Main track.}
  \label{fig:progress}
\end{figure}

\iffalse
\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015-2018 of all logics in the Application track.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_Application_Track_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics in the
  Application track.}
  \label{fig:progress}
\end{figure}
\fi
